Universal Anonymous Signatures

### 2022-09-16 prism-backend/research/gsac/formal-uas.tex
Minor changes.

\paragraph{Functional placeholders.} %
We use generic functions to capture, at the design level, that users need
to prove concrete claims over their private information. Looking a bit ahead,
the output of these functions is defined in terms of (subsets of) the users'
key, credentials and attributes, and signed message. But, during our modelling,
we are only concerned with preventing that the output of these functions can
be dishonestly altered, and with ensuring that it does not threaten privacy
beyond what is necessary or unavoidable to reach the flexibility we want.

@@

\begin{description}
\item[$\fissue: (\upk,\cid,\attrs,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]})
  \rightarrow \yissue$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  with identifier $\cid = (\cidi,\cidu)$, over attributes \attrs, when requested
  by a user with public key \upk,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
  $n$ may be $0$ if no previously obtained credential is used). \fissue returns
  a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
  convention that $\yissue = 0$ means that the issuance request is denied; and
  $\yissue \neq 0$ means that the request is approved. \fissue functions must be
  \UAS-acceptable, as defined in \defref{def:uas-acc-func}.
\item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user public key \upk, a set of credentials with identifiers
  and attributes $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
  values, $\yeval^0$ and $\yeval^1$. Both must belong in a well defined set
  \rngfeval. For readability, we write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\upk,\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

@@

Concerning \fissue functions, our \UAS model requires them to be \UAS-acceptable
functions. At a high level, this requires that \fissue functions do not reveal
anything about the signer's data used as input. This is formally captured in
\figref{fig:uas-acceptable}.

@@

A \UAS construction thus can only be secure if the \fissue function it uses is
\UAS-acceptable.
%
Next, we define the concept of \CUASGen restrictions. Briefly, these are special
cases of our generic construction that target a concrete variant of the
utility-privacy tradeoff by defining concrete \fissue, \feval and \finsp
functions. Security of \CUASGen implies security of its restrictions, as long as
the chosen \fissue functions are \CUASGen-acceptable.

>>>>

\paragraph{Functional placeholders.} %
We use generic functions to capture, at the design level, that users need
to prove concrete claims over their private information. Looking a bit ahead,
the output of these functions is defined in terms of (subsets of) the users'
key, credentials and attributes, and signed message. But, during our modelling,
we are only concerned with preventing that the output of these functions can
be altered, and with ensuring that it does not threaten privacy beyond what is
necessary or unavoidable to reach the flexibility we want.

@@

\begin{description}
\item[$\fissue: (\upk,\cid,\attrs,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]})
  \rightarrow \yissue$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the conditions required by the issuer to grant a credential
  with identifier $\cid = (\cidi,\cidu)$, over attributes \attrs, when requested
  by a user with public key \upk, leveraging a set of $n$ previously obtained
  credentials with identifiers and attributes given by $\lbrace (\cid_i,
  \cattrs_i) \rbrace_{i \in [n]}$ (where $n$ may be $0$). \fissue returns
  a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
  convention that $\yissue = 0$ means that the issuance request is denied; and
  $\yissue \neq 0$ means that the request is approved. \fissue functions must be
  \UAS-acceptable, as defined in \defref{def:uas-acc-func}.
\item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user public key \upk, a set of credentials with identifiers
  and attributes $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
  values, $\yeval^0$ and $\yeval^1$. Both must belong in a well defined set
  \rngfeval. For readability, we write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\upk,\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

@@

Concerning \fissue functions, our \UAS model requires them to be
\UAS-acceptable. At a high level, this requires that \fissue functions do not
reveal anything about the signer's data used as input. This is formally captured
in \figref{fig:uas-acceptable}.
%
A \UAS construction thus can only be secure if the \fissue functions it uses
are \UAS-acceptable.

@@

Next, we define the concept of \CUASGen restrictions. These are special
cases of our generic construction that target a concrete variant of the
utility-privacy tradeoff by defining concrete \fissue, \feval and \finsp
functions. Security of \CUASGen implies security of its restrictions, if
the chosen \fissue functions are \CUASGen-acceptable.
